Hierarchical Control for Aircraft Electronic Power Systems

### 2012-12-08 project/report/paper.tex
fixed 'spill' of section 7.2 title
ref

Notice the integral from time $t$ to time $t+horizon$. 
If the horizon=1, then we simply optimize the objective function for one system timestep.
However, if the horizon=10, then we do one call to the CPLEX MILP solver to compute the optimal system configurations for 10 timesteps.
Batching several timesteps into one MILP call can reduce the overall computation time: using a 6-core Intel 3930K processor, optimizing 1 timestep takes an average of 350ms, while optimizing 10 timesteps takes an average of 500ms (so, 50ms per timestep in the batched configuration).

@@

\subsection{Example: LL-LMS Preserves Safety in Power Spike}
\label{sec:power-spike-example}
In this example, we show how the Hierarchical LMS preserves safety when the live workload data demands more power than the historical data predicts. 
At Timestep 1 in the following tables, the live data matches the historical data, and the Optimizing LMS provides safe advice.
However, Timestep 2 has a power spike in Load 3 that is not anticipated in the historical data. 
Relying on the Optimizing-LMS alone at Timestep 2 would result in an unsafe configuration, where 120,000W is draw, while the generator can only produce 100,000W.
Fortunately, the LL-LMS in our Hierarchical controller observes the Load 3 power spike in real-time, and it sheds Load 3 to maintain safety, thus maintaining a total power draw of 80,000W, which is within the generator's 100,000W power cap.

>>>>

Notice the integral from time $t$ to time $t+horizon$. 
If the horizon=1, then we simply optimize the objective function for one system timestep.
However, if the horizon=10, then we do one call to the CPLEX~\cite{CPLEX} MILP solver to compute the optimal system configurations for 10 timesteps.
Batching several timesteps into one MILP call can reduce the overall computation time: using a 6-core Intel 3930K processor, optimizing 1 timestep takes an average of 350ms, while optimizing 10 timesteps takes an average of 500ms (so, 50ms per timestep in the batched configuration).

@@

\subsection{Example: LL-LMS Preserves Safety in \\ Power Spike}
\label{sec:power-spike-example}
In this example, we show how the Hierarchical LMS preserves safety when the live workload data demands more power than the historical data predicts. 
At Timestep 1 in the following tables, the live data matches the historical data, and the Optimizing LMS provides safe advice.
However, Timestep 2 has a power spike in Load 3 that is not anticipated in the historical data. 
Relying on the Optimizing-LMS alone at Timestep 2 would result in an unsafe configuration, where 120,000W is draw, while the generator can only produce 100,000W.
Fortunately, the LL-LMS in our Hierarchical controller observes the Load 3 power spike in real-time, and it sheds Load 3 to maintain safety, thus maintaining a total power draw of 80,000W, which is within the generator's 100,000W power cap.
